---
title: "Phoenix_housing_data_cleaning"
author: "Masaaki Kato"
date: "2/26/2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(dplyr)
library(tidyverse)
library(readr)
library(ggplot2)
library(gridExtra)
```
## R Markdown

```{r DataLoading, include=TRUE}
# load data

# demographic data
sex_by_age <- read_csv("phoenix-az-sex-by-age.csv", show_col_types = FALSE)
sex_by_edu <- read_csv("phoenix-az-sex-by-educational-attainment-for-the-population-25-years-and-over.csv", show_col_types = FALSE)

# housing data
tenure <- read_csv("phoenix-az-tenure.csv", show_col_types = FALSE)
occupancy_status <- read_csv("phoenix-az-occupancy-status.csv", show_col_types = FALSE)

# economic data
poverty_status <- read_csv("phoenix-az-poverty-status.csv", show_col_types = FALSE)
median_gross_rent <- read_csv("phoenix-az-median-gross-rent.csv", show_col_types = FALSE)
median_income <- read_csv("phoenix-az-median-household-income.csv", show_col_types = FALSE)
```

## Data Cleaning:
- The `poverty_status` table contains many unnecessary columns
  - only include information for male/female age 18+
  - split information for male and female 
  - rename columns for easy view
  
```{r DataCleaning1.4, include=TRUE}
poverty_status_male <- subset(poverty_status, select=c("geoid",
                                                       "year",
                                                       "Income at or above poverty level - Male",
                                                      "Income below poverty level - Male",
                                                      "Income at or above poverty level - Male - 18 to 24 years",
                                                      "Income at or above poverty level - Male - 25 to 34 years",
                                                      "Income at or above poverty level - Male - 35 to 44 years",
                                                      "Income at or above poverty level - Male - 45 to 54 years",
                                                      "Income at or above poverty level - Male - 55 to 64 years",
                                                      "Income at or above poverty level - Male - 75 years and over",
                                                      "Income below poverty level - Male - 18 to 24 years",
                                                      "Income below poverty level - Male - 25 to 34 years",
                                                      "Income below poverty level - Male - 35 to 44 years",
                                                      "Income below poverty level - Male - 45 to 54 years",
                                                      "Income below poverty level - Male - 55 to 64 years",
                                                      "Income below poverty level - Male - 75 years and over"))
names(poverty_status_male) <- c("geoid",
                                "year",
                                "male_income_above_total",
                                "male_income_below_total",
                                "male_income_above_18_24",
                                "male_income_above_25_34",
                                "male_income_above_35_44",
                                "male_income_above_45_54",
                                "male_income_above_55_64",
                                "male_income_above_75_and_above",
                                "male_income_below_18_24",
                                "male_income_below_25_34",
                                "male_income_below_35_44",
                                "male_income_below_45_54",
                                "male_income_below_55_64",
                                "male_income_below_75_and_above")

poverty_status_female <- subset(poverty_status, select=c("geoid",
                                                       "year",
                                                       "Income at or above poverty level - Female",
                                                      "Income below poverty level - Female",
                                                      "Income at or above poverty level - Female - 18 to 24 years",
                                                      "Income at or above poverty level - Female - 25 to 34 years",
                                                      "Income at or above poverty level - Female - 35 to 44 years",
                                                      "Income at or above poverty level - Female - 45 to 54 years",
                                                      "Income at or above poverty level - Female - 55 to 64 years",
                                                      "Income at or above poverty level - Female - 75 years and over",
                                                      "Income below poverty level - Female - 18 to 24 years",
                                                      "Income below poverty level - Female - 25 to 34 years",
                                                      "Income below poverty level - Female - 35 to 44 years",
                                                      "Income below poverty level - Female - 45 to 54 years",
                                                      "Income below poverty level - Female - 55 to 64 years",
                                                      "Income below poverty level - Female - 75 years and over"))
names(poverty_status_female) <- c("geoid",
                                "year",
                                "female_income_above_total",
                                "female_income_below_total",
                                "female_income_above_18_24",
                                "female_income_above_25_34",
                                "female_income_above_35_44",
                                "female_income_above_45_54",
                                "female_income_above_55_64",
                                "female_income_above_75_and_above",
                                "female_income_below_18_24",
                                "female_income_below_25_34",
                                "female_income_below_35_44",
                                "female_income_below_45_54",
                                "female_income_below_55_64",
                                "female_income_below_75_and_above")
poverty_status_male[1:3,2:6]
```

- The `sex_by_age` table contains unnecessary columns as well
  - add people, 17 and below, into one column `sex_17_and_below`
  - group people by age brackets similar to `poverty_status` (e.g., 18-24, 25-34, 45-54)
  - split information by sex

```{r DataCleaning2, include=TRUE}
sex_by_age_temp <- sex_by_age
names(sex_by_age_temp) <- str_replace_all(names(sex_by_age_temp), c(" " = "_")) # replace spaces with underscore in column names

# re-categorizing age brackets
sex_by_age_temp$male_17_and_below <- (sex_by_age_temp$Male_Under_5_years + sex_by_age_temp$Male_5_to_9_years 
                                    + sex_by_age_temp$Male_10_to_14_years + sex_by_age_temp$Male_15_to_17_years)
sex_by_age_temp$male_18_24 <- (sex_by_age_temp$Male_18_and_19_years + sex_by_age_temp$Male_20_years
                             + sex_by_age_temp$Male_21_years + sex_by_age_temp$Male_22_to_24_years)
sex_by_age_temp$male_25_34 <- (sex_by_age_temp$Male_25_to_29_years + sex_by_age_temp$Male_30_to_34_years)
sex_by_age_temp$male_35_44 <- (sex_by_age_temp$Male_35_to_39_years + sex_by_age_temp$Male_40_to_44_years)
sex_by_age_temp$male_45_54 <- (sex_by_age_temp$Male_45_to_49_years + sex_by_age_temp$Male_50_to_54_years)
sex_by_age_temp$male_55_64 <- (sex_by_age_temp$Male_55_to_59_years + sex_by_age_temp$Male_60_and_61_years 
                             + sex_by_age_temp$Male_62_to_64_years)
sex_by_age_temp$male_65_74 <- (sex_by_age_temp$Male_65_and_66_years + sex_by_age_temp$Male_67_to_69_years
                            + sex_by_age_temp$Male_70_to_74_years)
sex_by_age_temp$male_75_and_above <- (sex_by_age_temp$Male_75_to_79_years + sex_by_age_temp$Male_80_to_84_years
                                    + sex_by_age_temp$Male_85_years_and_over)

sex_by_age_temp$female_17_and_below <- (sex_by_age_temp$Female_Under_5_years + sex_by_age_temp$Female_5_to_9_years 
                                    + sex_by_age_temp$Female_10_to_14_years + sex_by_age_temp$Female_15_to_17_years)
sex_by_age_temp$female_18_24 <- (sex_by_age_temp$Female_18_and_19_years + sex_by_age_temp$Female_20_years
                             + sex_by_age_temp$Female_21_years + sex_by_age_temp$Female_22_to_24_years)
sex_by_age_temp$female_25_34 <- (sex_by_age_temp$Female_25_to_29_years + sex_by_age_temp$Female_30_to_34_years)
sex_by_age_temp$female_35_44 <- (sex_by_age_temp$Female_35_to_39_years + sex_by_age_temp$Female_40_to_44_years)
sex_by_age_temp$female_45_54 <- (sex_by_age_temp$Female_45_to_49_years + sex_by_age_temp$Female_50_to_54_years)
sex_by_age_temp$female_55_64 <- (sex_by_age_temp$Female_55_to_59_years + sex_by_age_temp$Female_60_and_61_years
                            + sex_by_age_temp$Female_62_to_64_years)
sex_by_age_temp$female_65_74 <- (sex_by_age_temp$Female_65_and_66_years + sex_by_age_temp$Female_67_to_69_years
                            + sex_by_age_temp$Female_70_to_74_years)
sex_by_age_temp$female_75_and_above <- (sex_by_age_temp$Female_75_to_79_years + sex_by_age_temp$Female_80_to_84_years
                                    + sex_by_age_temp$Female_85_years_and_over)

# subset only necessary columns
sex_by_age_cleaned <- subset(sex_by_age_temp, select=c("geoid",
                                                       "year",
                                                       "male_17_and_below",
                                                       "male_18_24",
                                                       "male_25_34",
                                                       "male_35_44",
                                                       "male_45_54",
                                                       "male_55_64",
                                                       "male_65_74",
                                                       "male_75_and_above",
                                                       "female_17_and_below",
                                                       "female_18_24",
                                                       "female_25_34",
                                                       "female_35_44",
                                                       "female_45_54",
                                                       "female_55_64",
                                                       "female_65_74",
                                                       "female_75_and_above"))

# split info by sex
sex_by_age_male <- subset(sex_by_age_cleaned, select=c("geoid",
                                                       "year",
                                                       "male_17_and_below",
                                                       "male_18_24",
                                                       "male_25_34",
                                                       "male_35_44",
                                                       "male_45_54",
                                                       "male_55_64",
                                                       "male_65_74",
                                                       "male_75_and_above"))

sex_by_age_female <- subset(sex_by_age_cleaned, select=c("geoid",
                                                         "year",
                                                         "female_17_and_below",
                                                         "female_18_24",
                                                         "female_25_34",
                                                         "female_35_44",
                                                         "female_45_54",
                                                         "female_55_64",
                                                         "female_65_74",
                                                         "female_75_and_above"))
sex_by_age_cleaned[1:3,2:6]
```

- The `sex_by_edu` table contains unnecessary columns as well
  - only include education from highshcool and above
  - split information by sex

```{r DataCleaning5}

sex_by_edu_cleaned <- subset(sex_by_edu, select=c("geoid",
                                                  "year",
                                                  "Male - 12th grade, no diploma",
                                                  "Male - High school graduate, GED, or alternative",
                                                  "Male - Some college, less than 1 year",
                                                  "Male - Some college, 1 or more years, no degree",
                                                  "Male - Associate's degree",
                                                  "Male - Bachelor's degree",
                                                  "Male - Master's degree",
                                                  "Male - Professional school degree",
                                                  "Male - Doctorate degree",
                                                  "Female - 12th grade, no diploma",
                                                  "Female - High school graduate, GED, or alternative",
                                                  "Female - Some college, less than 1 year",
                                                  "Female - Some college, 1 or more years, no degree",
                                                  "Female - Associate's degree",
                                                  "Female - Bachelor's degree",
                                                  "Female - Master's degree",
                                                  "Female - Professional school degree",
                                                  "Female - Doctorate degree"))
names(sex_by_edu_cleaned) <- c("geoid",
                               "year",
                               "male_12th_grade_no_diploma",
                               "male_hs_graduate_ged_alt",
                               "male_college_less_than_1_year",
                               "male_college_1_or_more_year",
                               "male_associate_degree",
                               "male_bachelor_degree",
                               "male_master_degree",
                               "male_professional_school_degree",
                               "male_doctorate_degree",
                               "female_12th_grade_no_diploma",
                               "female_hs_graduate_ged_alt",
                               "female_college_less_than_1_year",
                               "female_college_1_or_more_year",
                               "female_associate_degree",
                               "female_bachelor_degree",
                               "female_master_degree",
                               "female_professional_school_degree",
                               "female_doctorate_degree")

# seperate info by sex
sex_by_edu_male <- subset(sex_by_edu_cleaned, select=c("geoid",
                                                       "year",
                                                       "male_12th_grade_no_diploma",
                                                       "male_hs_graduate_ged_alt",
                                                       "male_college_less_than_1_year",
                                                       "male_college_1_or_more_year",
                                                       "male_associate_degree",
                                                       "male_bachelor_degree",
                                                       "male_master_degree",
                                                       "male_professional_school_degree",
                                                       "male_doctorate_degree"))
sex_by_edu_female <- subset(sex_by_edu_cleaned, select=c("geoid",
                                                         "year",
                                                         "female_12th_grade_no_diploma",
                                                         "female_hs_graduate_ged_alt",
                                                         "female_college_less_than_1_year",
                                                         "female_college_1_or_more_year",
                                                         "female_associate_degree",
                                                         "female_bachelor_degree",
                                                         "female_master_degree",
                                                         "female_professional_school_degree",
                                                         "female_doctorate_degree"))
sex_by_edu_cleaned[1:3,2:6]
```

- Renaming column names for `tenure`, `median_gross_rent`, and `median_income`. Mainly removing spaces

```{r DataCleaning, include=TRUE}
# Renaming columns (i.e., removing spaces)
tenure_cleaned <- tenure
names(tenure_cleaned) <- c("geoid", "year", "owner_occupied", "renter_occupied")

median_gross_rent_cleaned <- median_gross_rent
names(median_gross_rent_cleaned) <- c("geoid","year","median_gross_rent")

median_income_cleaned <- median_income
names(median_income_cleaned) <- c("geoid","year","median_income")

occupancy_status_cleaned <- occupancy_status
names(occupancy_status_cleaned) <- c("geoid", "year", "total_housing_units", "occupied_housing_units", "vacant_housing_units")
```

## Visual Graphics

```{r simplePlot}
# plot of tenure status 
legends_tenure <- c("Renter Occupied"="#808080","Owner Occupied"="#0000FF")
ggplot(data=tenure_cleaned, aes(x=year)) + 
       geom_line(aes(y =owner_occupied,colour="#0000FF"),colour="#0000FF", size=1.5) + 
       geom_line(aes(y=renter_occupied,colour="#808080"), size=1.5) +
       scale_x_discrete(limits = c(2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019, 2020), 
                        expand=expansion(mult=c(0.1, .1))) + 
       scale_colour_manual(name="Variable",values = legends_tenure) +
       labs(title="Tenure Status", subtitle="Pheonix, Arizona", x="Year", y="Households") +
       theme(plot.title = element_text(hjust = 0.5),
             plot.subtitle = element_text(hjust = 0.5))

```


```{r Plot1, include=TRUE}

# plot of median gross rent
ggplot(data=median_gross_rent_cleaned, aes(x=year,y=median_gross_rent)) +
       geom_line(colour='blue', size=1.5) +
       scale_x_discrete(limits = c(2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019, 2020), 
                        expand=expansion(mult=c(0.1, .1))) + 
       labs(title="Median Gross Rent", subtitle="Pheonix, Arizona", x="Year", y="Median Gross Rent") +
       theme(plot.title = element_text(hjust = 0.5),
             plot.subtitle = element_text(hjust = 0.5))
```


```{r Plot2, include=TRUE}

# plot of median income
ggplot(data=median_income_cleaned, aes(x=year,y=median_income)) +
       geom_line(colour='blue', size=1.5) +
       scale_x_discrete(limits = c(2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019, 2020), 
                        expand=expansion(mult=c(0.1, .1))) + 
       labs(title="Median Income", subtitle="Pheonix, Arizona", x="Year", y="Median Income") +
       theme(plot.title = element_text(hjust = 0.5),
             plot.subtitle = element_text(hjust = 0.5))
```


```{r Plot3, include=TRUE}

# plot of occupancy status
occupied_plot <- ggplot(data=occupancy_status_cleaned, aes(x=year,y=occupied_housing_units)) +
                       geom_line(colour='blue', size=1.5) +
                       scale_x_discrete(limits = c(2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019, 2020),
                                        expand=expansion(mult=c(0.1, .1))) + 
                       labs(title="Occupancy Status", subtitle="Pheonix, Arizona", x="", y="Occupied Housing Units") +
                       theme(plot.title = element_text(hjust = 0.5),
                             plot.subtitle = element_text(hjust = 0.5))
vacant_plot <- ggplot(data=occupancy_status_cleaned, aes(x=year,y=vacant_housing_units)) +
                      geom_line(colour='blue', size=1.5) +
                      scale_x_discrete(limits = c(2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019, 2020),
                                       expand=expansion(mult=c(0.1, .1))) + 
                      labs(x="Year", y="Vacant Housing Units") +
                      theme(plot.title = element_text(hjust = 0.5),
                            plot.subtitle = element_text(hjust = 0.5))

# plot side by side
grid.arrange(occupied_plot, vacant_plot)
```

### Sex by Education
```{r plot4}

# format data
# Format Data to convert each education degree as a categorical variable
sex_by_edu_male_long <- sex_by_edu_male %>%
  pivot_longer(male_12th_grade_no_diploma:male_doctorate_degree, names_to = "education", values_to = "population")

# subsetting data because population differences is too wide between some degrees
sex_by_edu_male_long1 <- subset(sex_by_edu_male_long, education %in% c("male_bachelor_degree",
                                                                    "male_college_1_or_more_year",
                                                                    "male_hs_graduate_ged_alt") )
sex_by_edu_male_long2 <- subset(sex_by_edu_male_long, education %in% c("male_12th_grade_no_diploma",
                                                                    "male_college_less_than_1_year",
                                                                    "male_associate_degree",
                                                                    "male_professional_school_degree",
                                                                    "male_master_degree",
                                                                    "male_doctorate_degree") )

# plot graph
ggplot(data = sex_by_edu_male_long1, aes(year, population)) +
       geom_line(color = "steelblue", size = 1) +
       geom_point(color="steelblue") + 
       labs(title = "Educational Attainment (Male)",
            subtitle = "Pheonix, Arizona",
            y = "Population", x = "Year") + 
       facet_wrap(~ education) +
       theme(plot.title = element_text(hjust = 0.5),
             plot.subtitle = element_text(hjust = 0.5))
ggplot(data = sex_by_edu_male_long2, aes(year, population)) +
       geom_line(color = "steelblue", size = 1) +
       geom_point(color="steelblue") + 
       labs(title = "Educational Attainment (Male)",
            subtitle = "Population, Arizona",
            y = "Population", x = "Year") + 
       facet_wrap(~ education) +
       theme(plot.title = element_text(hjust = 0.5),
             plot.subtitle = element_text(hjust = 0.5))
```

```{r Plot5, include=TRUE}
# Format Data to convert each education degree as a categorical variable
sex_by_edu_female_long <- sex_by_edu_female %>%
  pivot_longer(female_12th_grade_no_diploma:female_doctorate_degree, names_to = "education", values_to = "population")

# subsetting data because population differences is too wide between some degrees
sex_by_edu_female_long1 <- subset(sex_by_edu_female_long, education %in% c("female_bachelor_degree",
                                                                    "female_college_1_or_more_year",
                                                                    "female_hs_graduate_ged_alt") )
sex_by_edu_female_long2 <- subset(sex_by_edu_female_long, education %in% c("male_12th_grade_no_diploma",
                                                                    "female_college_less_than_1_year",
                                                                    "female_associate_degree",
                                                                    "female_professional_school_degree",
                                                                    "female_master_degree",
                                                                    "female_doctorate_degree") )

# plot graph
ggplot(data = sex_by_edu_female_long1, aes(year, population)) +
       geom_line(color = "steelblue", size = 1) +
       geom_point(color="steelblue") + 
       labs(title = "Educational Attainment (Female)",
            subtitle = "Pheonix, Arizona",
            y = "Population", x = "Year") + 
       facet_wrap(~ education) +
       theme(plot.title = element_text(hjust = 0.5),
             plot.subtitle = element_text(hjust = 0.5))
ggplot(data = sex_by_edu_female_long2, aes(year, population)) +
       geom_line(color = "steelblue", size = 1) +
       geom_point(color="steelblue") + 
       labs(title = "Educational Attainment (Female)",
            subtitle = "Population, Arizona",
            y = "Population", x = "Year") + 
       facet_wrap(~ education)  +
       theme(plot.title = element_text(hjust = 0.5),
             plot.subtitle = element_text(hjust = 0.5))
```

### Sex by age

```{r plot6, include=TRUE}
# plot for sex by age
# Format Data to convert each age bracket as a categorical variable
sex_by_age_female_long <- sex_by_age_female %>%
  pivot_longer(female_17_and_below:female_75_and_above, names_to = "age_bracket", values_to = "population")

# plot graph
ggplot(data = sex_by_age_female_long, aes(year, population)) +
       geom_line(color = "steelblue", size = 1) +
       geom_point(color="steelblue") + 
       labs(title = "Age Bracket (Female)",
            subtitle = "Pheonix, Arizona",
            y = "Population", x = "Year") + 
       facet_wrap(~ age_bracket)  +
       theme(plot.title = element_text(hjust = 0.5),
             plot.subtitle = element_text(hjust = 0.5))

```

```{r echo, include=TRUE}
# plot for sex by age
# Format Data to convert each age bracket as a categorical variable
sex_by_age_male_long <- sex_by_age_male %>%
  pivot_longer(male_17_and_below:male_75_and_above, names_to = "age_bracket", values_to = "population")

# plot graph
ggplot(data = sex_by_age_male_long, aes(year, population)) +
       geom_line(color = "steelblue", size = 1) +
       geom_point(color="steelblue") + 
       labs(title = "Age Bracket (Male)",
            subtitle = "Pheonix, Arizona",
            y = "Population", x = "Year") + 
       facet_wrap(~ age_bracket)  +
       theme(plot.title = element_text(hjust = 0.5),
             plot.subtitle = element_text(hjust = 0.5))
```

### Poverty Status by Sex
```{r plot7, include=TRUE}
# plot for sex by poverty status (above poverty, below poverty)
# Format Data to convert each poverty status as a categorical variable
poverty_status_male_long_above <- poverty_status_male %>%
  pivot_longer(male_income_above_18_24:male_income_above_75_and_above, names_to = "age_bracket", values_to = "population")
poverty_status_male_long_below <- poverty_status_male %>%
  pivot_longer(male_income_below_18_24:male_income_below_75_and_above, names_to = "age_bracket", values_to = "population")


# plot graph
ggplot(data = poverty_status_male_long_above, aes(year, population)) +
       geom_line(color = "steelblue", size = 1) +
       geom_point(color="steelblue") + 
       labs(title = "Age Bracket for Males Above Poverty",
            subtitle = "Pheonix, Arizona",
            y = "Population", x = "Year") + 
       facet_wrap(~ age_bracket)  +
       theme(plot.title = element_text(hjust = 0.5),
             plot.subtitle = element_text(hjust = 0.5))

ggplot(data = poverty_status_male_long_below, aes(year, population)) +
       geom_line(color = "steelblue", size = 1) +
       geom_point(color="steelblue") + 
       labs(title = "Age Bracket for Males Below Poverty",
            subtitle = "Pheonix, Arizona",
            y = "Population", x = "Year") + 
       facet_wrap(~ age_bracket)  +
       theme(plot.title = element_text(hjust = 0.5),
             plot.subtitle = element_text(hjust = 0.5))
```

```{r plot8, include=TRUE}
# plot for sex by poverty status (above poverty, below poverty)
# Format Data to convert each poverty status as a categorical variable
poverty_status_female_long_above <- poverty_status_female %>%
  pivot_longer(female_income_above_18_24:female_income_above_75_and_above, names_to = "age_bracket", values_to = "population")
poverty_status_female_long_below <- poverty_status_female %>%
  pivot_longer(female_income_below_18_24:female_income_below_75_and_above, names_to = "age_bracket", values_to = "population")


# plot graph
ggplot(data = poverty_status_female_long_above, aes(year, population)) +
       geom_line(color = "steelblue", size = 1) +
       geom_point(color="steelblue") + 
       labs(title = "Age Bracket (Male) for Above Poverty",
            subtitle = "Pheonix, Arizona",
            y = "Population", x = "Year") + 
       facet_wrap(~ age_bracket)  +
       theme(plot.title = element_text(hjust = 0.5),
             plot.subtitle = element_text(hjust = 0.5))

ggplot(data = poverty_status_female_long_below, aes(year, population)) +
       geom_line(color = "steelblue", size = 1) +
       geom_point(color="steelblue") + 
       labs(title = "Age Bracket (Male) for Below Poverty",
            subtitle = "Pheonix, Arizona",
            y = "Population", x = "Year") + 
       facet_wrap(~ age_bracket)  +
       theme(plot.title = element_text(hjust = 0.5),
             plot.subtitle = element_text(hjust = 0.5))
```

```{r ExportData, include=FALSE}
write_csv(poverty_status_male, "C:\\Users\\mkpanda\\Desktop\\dojo\\projects\\phoenix_housing_inR\\poverty_status_male.csv")
write_csv(poverty_status_female, "C:\\Users\\mkpanda\\Desktop\\dojo\\projects\\phoenix_housing_inR\\poverty_status_female.csv")

write_csv(sex_by_age_cleaned, "C:\\Users\\mkpanda\\Desktop\\dojo\\projects\\phoenix_housing_inR\\sex_by_age_cleaned.csv")
write_csv(sex_by_age_male, "C:\\Users\\mkpanda\\Desktop\\dojo\\projects\\phoenix_housing_inR\\sex_by_age_male.csv")
write_csv(sex_by_age_female, "C:\\Users\\mkpanda\\Desktop\\dojo\\projects\\phoenix_housing_inR\\sex_by_age_female.csv")
write_csv(sex_by_edu_cleaned, "C:\\Users\\mkpanda\\Desktop\\dojo\\projects\\phoenix_housing_inR\\sex_by_edu_cleaned.csv")
write_csv(sex_by_edu_male, "C:\\Users\\mkpanda\\Desktop\\dojo\\projects\\phoenix_housing_inR\\sex_by_edu_male.csv")
write_csv(sex_by_edu_female, "C:\\Users\\mkpanda\\Desktop\\dojo\\projects\\phoenix_housing_inR\\sex_by_edu_female.csv")

write_csv(tenure_cleaned, "C:\\Users\\mkpanda\\Desktop\\dojo\\projects\\phoenix_housing_inR\\tenure_cleaned.csv")
write_csv(median_gross_rent_cleaned, "C:\\Users\\mkpanda\\Desktop\\dojo\\projects\\phoenix_housing_inR\\median_gross_rent_cleaned.csv")
write_csv(median_income_cleaned, "C:\\Users\\mkpanda\\Desktop\\dojo\\projects\\phoenix_housing_inR\\median_income_cleaned.csv")
write_csv(occupancy_status_cleaned, "C:\\Users\\mkpanda\\Desktop\\dojo\\projects\\phoenix_housing_inR\\occupancy_status_cleaned.csv")
```
